---
title: 'Analysis of mtcars dataset using Shiny'
author: "Nanda kumar Sathiyamoorthy"
date: "August 14, 2017"
output: ioslides_presentation
---

## Introduction

- This is the final project of the Developing data products course on Coursera. 

- Here we demonstrate the use of Shiny by building an app to analyse the mtcars dataset. 

- Slidy has been used to create the presentation slides.

- Plotly has been used to make interactive plots in the Shiny application.

## mtcars Dataset

mtcars is an built-in data set in R that has been extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r}
head(mtcars)
```

## Correlation plot

```{r echo = FALSE}
library(corrplot)
```

```{r fig.height=4, fig.width=7}
corrplot(cor(mtcars))
```

## Shiny Application

The Shiny Application can be found here :

https://nandakumar212.shinyapps.io/DevelopingDataProductsShiny/

- Here we make scatterplots for the variables that user selects.
- Correlation between the selected variables are also calculated and displayed.
- Also, a data table corresponding to the subset of data being analysed is shown.